Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-10-16 writeups/dissertation/dissertation.tex
foo

In order to best combine these predictors, a logistic regression statistical technique similar to \textcite{Stanley2013} was used to determine the most optimal weights for each term.
Each term in the full model (see the total activation equation Table \ref{tabModACTRModel}) is weighted so that model accuracy is maximized.  
\textcite{Stanley2013} found that the optimal weights for the StackOverflow model for the prior term, title context term, and body context term were \num{.62}, \num{.93}, and \num{1.75} respectively.

The optimal weights for each model component are computed in the following way:
When a user creates a tag for a post, a retrieval request for the model is made.
For each request, the model returns a set of tags (all tags that have been observed for that user in the past) and activations associated with each tag.
An activation value is computed for each model component (e.g., prior tag use, context) for each tag.
These values are recorded, and tag instances that match what the author actually tagged are marked as a 1, while all others are marked with a 0.
This process is repeated across all posts where a user chooses a tag, and across all users in the dataset.
Once all of the results are aggregated, a logistic regression is run where the optimal weights for each model component are found that maximize the model's ability to correctly label tags as 0 or 1 based on total activation.

@@

A simplified version of \citeauthor{Stanley2013}'s method was used for the results for this research.
Instead of subtracting off the mean total activation for the top 5 tags for each post, the process is done in isolation for each model component.
So for the prior component, the activation value used in the logistic regression is the prior activation with the mean of the top 5 prior activations subtracted off of this value.
The same process is used for the context component.
Decoupling the offset term and computing an offset for each model component in isolation means that an iterative approach is no longer necessary,
since the optimal weights of the terms are no longer needed when computing the offset.

@@

The context component for both the random permutation and Bayesian model is based on the same co-occurrence matrix of words and observed tags.
Different size matrices were analyzed, ranging from \num{1000}, \num{10000}, \num{100000}, \num{1000000}, and \num{3000000} posts.
The matrix for \num{3000000} posts was only used for Twitter, since the number of words in a StackOverflow post is much higher than Twitter on average,
and the space and computational time required when using a co-occurrence matrix of \num{3000000} posts for StackOverflow is too high for a current high performance desktop, even with highly optimized representations.
Already \num{835500000} total co-occurring word tag observations were used to build a co-occurrence matrix of \num{1000000} StackOverflow posts.
It was also the case that \num{1000000} posts for StackOverflow was already around $1/7$ of the total posts created on the site,
so it is reasonable to assume that the results would not change greatly for StackOverflow if $3/7$ of the total posts created were used to build the co-occurrence matrix instead,
especially since \num{835500000} co-occurrences were already used with \num{1000000} posts.

@@

The impact of adding the offset to each of the models for StackOverflow and Twitter is shown in Figures \ref{figContextOffsetSO} and \ref{figContextOffsetT}.
In both plots, if the model name includes ``full'' then all model components are included.
When they are enumerated, then at least one of the components is left out.
The random permutation and Bayesian models are plotted alongside each other so that comparisons across the two model types can be done easily.
So, for example, the ``standard prior model relaxed across posts without offset'' means that only the prior model component was used and the offset for that component was not subtracted off when determining activation.
As another example, the ``Bayes only orderless context'' means that only the context component of the Bayesian model was used (along with the offset), and that no order information was used for that contextual component term.

@@

The random permutation model in particular is greatly affected by the offset term, for both the StackOverflow and Twitter.
This suggests that the mean activation for the random permutation model for the top few tags in each post can vary greatly across posts.
Only if this mean activation is subtracted off will the logistic regression model generate optimal weights and predictions that are comparative to the Bayesian model when model accuracy relaxed across posts is examined.

@@

One simple and likely explanation is that there are posts where a large set of tags have high activation,
but the author is choosing to use only a fixed small set of the top tags for each post, regardless of the activation values of the top tags.
The author determines the number of tags to use for a post based on competing goals of tagging posts an not overly saturating a post with tags.
For example, the author may be writing a question on StackOverflow about \emph{javascript}, and a large set of related tags are retrieved from declarative memory that are all above the retrieval threshold
(e.g., \emph{javascript}, \emph{dom}, \emph{svg}, \emph{html}, \emph{jquery}, \emph{css}),
but the author only chooses to use the tags \emph{javascript}, \emph{dom}, and \emph{svg}, since he has decided to tag this post with three tags, and those are the three tags with the highest activation.
Adding the offset term into the model is a way to implement a simple version of this strategy where the author is actively choosing to use only a small set of tags for each post.

@@

The four subsets were collected across a period of one month.
Each was collected sequentially, and about one subset was collected per week.
The hashtags used in each subset were chosen by scraping a site that published the current trending hashtags for each city.
Before starting to collect for each subset, the current trending popular hashtags for each US city were collected, and then 400 were randomly sampled from this set.
Only 400 were selected since this is the maximum that the Twitter API can monitor at one time.

@@

Model accuracy results for components of both the random permutation and Bayesian models grouped by Twitter popular-hashtags subset are included in Figure \ref{figContextSubsets}.
Accuracy is affected significantly by subset ($F(3, 340) = 764, p < .001$)), model ($F(4, 340) = 3617, p < .001$), and the interaction between model and subset ($F(12, 340) = 142, p < .001$).
However, the effect size of model type on accuracy is \num{8.6} times larger than the interaction term ($\eta ^ {2} = 0.77$ versus $\eta ^ {2} = 0.090$).
This shows that the performance of a model relative to the other models remains consistent across the four subsets.
Further, the effect size of model type is \num{6.3} times larger than the effect of Twitter subset ($\eta ^ {2} = 0.770$ versus $\eta ^ {2} = 0.122$).
This shows that not only is relative model performance maintained across Twitter subsets, but the exact value of model accuracy for each model remains reasonably consistent across subsets.

@@

The first architectural concern examined how the method of handling stop words influenced model accuracy. 
\textcite{Sahlgren2008} looked at several ways to handle the commonly-occurring stop words for the random permutation model:
A data-driven frequency-weighted approach was tried, along with using a previously-derived stoplist, and no stop word removal at all.
Removing the high-frequency words in the dataset showed the highest performance increase compared to no stop word removal, and using a previously-derived stoplist hardly increased performance.
However, \citeauthor{Sahlgren2008} did not try to weight the stop words and only tried methods to remove them.
So alongside looking at frequency weighting, previously derived, and no stop word removal, \textcite{Stanley2013}'s method of attenuating stop words based on entropy was also explored.

@@

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{memMatSO-crop.pdf}}}
  \caption{Variance in observation counts of words for each tag for StackOverflow}
  \label{figContextCutoffSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{memMatT-crop.pdf}}}
  \caption{Variance in observation counts of words for each tag for Twitter}
  \label{figContextCutoffT}
\end{figure}

@@

The three stop word techniques were then tested for the random permutation model on the Twitter dataset, and the results are included in Figure \ref{figContextStopRPT}.
For the random permutation model for Twitter, the entropy weighting technique is the best method for handling stop words (\numNoZero{.25} to \numNoZero{.26}).
Removing stop-words based on a predetermined list actually decreases accuracy (\numNoZero{.25} to \numNoZero{.23}), and using data-driven frequency filtering has only a small to no effect (\numNoZero{.25} to \numNoZero{.25}).

@@

Since accuracy measurements when using a predetermined list to remove stop words for the random permutation model were much worse than the frequency and entropy methods, this method was not examined for the Bayesian model.
The results for the frequency and entropy techniques for the Bayesian model on the StackOverflow dataset are included in Figure \ref{figContextStopBSO}.

@@

\subsection{Dataset Size}

The second architectural concern examined how the number of documents used to build the co-occurrence matrix influenced model accuracy.
The default number of documents used to build the co-occurrence matrix was \num{1000000} for StackOverflow and \num{3000000} for Twitter.
In order to see how accuracy changed as function of document size, 
co-occurrence matrices for a range of smaller document sizes were built.
Both the random permutation and Bayesian models were tested on all document sizes.

@@

Model accuracy as a function of co-occurrence matrix size for StackOverflow is included in Figure \ref{figContextDocumentSizeSO}.
Accuracy improves for both the Bayesian and random permutation models as the size of the documents used to generate the co-occurrence matrix increases.
However, model accuracy using the entropy weighting technique plateaus and slightly decreases for the largest document size for the random permutation model, while the frequency technique only begins to plateau. 
The Bayesian model does not plateau and accuracy continues to improve as document size increases.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-freqVsEntropyBySizeSO-crop.pdf}}}
  \caption{Effect of size of co-occurrence matrix for StackOverflow}
  \label{figContextDocumentSizeSO}
\end{figure}

@@

It is likely that the random permutation model is starting to saturate when entropy weighting is used for the largest document size for StackOverflow.
Saturation happens when certain words co-occur with a tag much more often than all of the other words.
This introduces range effects when the correlation is computed, which ends up driving all of the correlations near one, and consequently decreases discrimination and accuracy.
Saturation happens when entropy weighting is used because the non-predictive words are only attenuated and not removed, and this attenuation is not enough to overcome the range effects that grow with document size.

@@

The overall trend of increasing accuracy with document size is present for Twitter as well.
Both entropy weighting and frequency filtering in Figure \ref{figContextDocumentSizeT} plateau for the random permutation model with increasing document size.
Once again, the Bayesian model continues to improve with document size.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-freqVsEntropyBySizeT-crop.pdf}}}
  \caption{Effect of size of co-occurrence matrix for Twitter}
  \label{figContextDocumentSizeT}
\end{figure}

@@

It is interesting to compare model accuracy between the Bayesian and random permutation model at the smallest and largest document sizes for both StackOverflow and Twitter.
At smaller document sizes, the random permutation model outperforms the Bayesian model (slightly for Twitter, dramatically for StackOverflow), and this performance difference deteriorates as document size increases.
In other words, the Bayesian model needs larger co-occurrence matrices than the random permutation model to work properly.
As the size of the dataset increases, the compression may start to lose crucial information, and the uncompressed Bayesian model should be used.
As the size of the dataset decreases, the noise and crosstalk introduced by the compression for the random permutation model is actually beneficial, and the compressed random permutation model should be used. 
This noise is beneficial because it helps soften spurious $S_{ji}$ values when the counts for each individual cell in the co-occurrence matrix are still volatile, which happens at smaller document sizes.

This result has important implications.
The document size is rarely chosen, and more likely constrained by the number of documents in the dataset being studied.
If that dataset is relatively small, it may be better to use the compressed random permutation model than the Bayesian model, and vice-versa if the dataset is large.

However, document size is not the only factor that determines whether the Bayesian model or random permutation model will perform better.
For example, the document size where the Bayesian model begins to outperform the random permutation model is quite different for StackOverflow and Twitter.
This is because the number of observations used to generate the co-occurrence matrix is a function of four components:
document size, number of words in each document, total number of unique tags, and number of tags used per document.
The average number of tags used per post for StackOverflow and Twitter were the same order of magnitude (around 3 for StackOverflow, slightly less for Twitter).

However, the average number of words in a StackOverflow post is much greater than the 140 character limit used for tweets.
More words per post means that the number of observations per cell in the co-occurrence matrix grows more quickly with document size.
The Bayesian model is more likely to perform better with datasets like StackOverflow that have these larger document sizes.

@@

The compressed random permutation model should perform better with smaller document sizes, less words per document, more unique tags, and fewer number of tags per post.
However, since there are so many factors that determine whether the Bayesian or random permutation model will perform better,
and only two different datasets were examined in this research,
it is difficult to make any specific recommendations as far as exact transition cut points (e.g., document size, words per document) where either the Bayesian or random permutation model should be used.
Also, it is likely that the specific domain being studied interacts with the factors already mentioned to determine which model is better for that domain.
Nevertheless, if a researcher is working in a domain with limited data (e.g., small document size, large tag space) that produces a sparse co-occurrence matrix,
then it may be worthwhile to experiment with using a compressed random permutation model instead of the full Bayesian model.

@@

Results for using different levels of compression for the random permutation model for the StackOverflow dataset are included in Figure \ref{figContextDimSO}.
In the figure, the model name that does not have the number of rows in the matrix specified is the \num{2048}-row matrix.
This was done so that names in all of the plots would remain consistent across all plots, and the \num{2048}-row matrix is the size used for the random permutation model for all other results.
The plot is also broken out for different size datasets used to build the co-occurrence matrix.

@@

Reducing compression to only 100 rows in the representation has a strong negative effect on accuracy (\numNoZero{.60} to \numNoZero{.55} for the \num{1000000} document dataset size).
But \num{2048} rows is sufficient for these datasets,
as increasing the number of rows to almost an order of magnitude higher (\num{10000}) has little to no positive impact on accuracy (\numNoZero{.60} to \numNoZero{.60} for the \num{1000000} document size).

Results are similar for Twitter.
Figure \ref{figContextDimT} shows the same negative impact when reducing from \num{2048} to \num{100} (\numNoZero{.26} to \numNoZero{.24} for the \num{3000000} document size),
and little to no impact when increasing from \num{2048} to \num{10000} (\numNoZero{.26} to \numNoZero{.26} at \num{3000000}).
This results are consistent across all document sizes used to build the co-occurrence matrix.

@@

The fact that the random permutation model only needs around \num{2048} rows to represent all of the words in the Twitter and StackOverflow datasets is impressive.
Twitter has around \num{2383000} unique words for the \num{3000000} tweets in each of the popular-users datasets.
StackOverflow has \num{5848000} unique words for the \num{1000000} posts used to generate the co-occurrence matrix.
So it is impressive that only \num{2048} rows are needed to represent most of the variance from all of the words in these co-occurrence matrices.
This is likely because word use frequency for StackOverflow and Twitter approximately follows Zipf's law \parencite{Stanley2013}.
This means that if the words are rank sorted by number of times they are used, the frequency of word use drops off sharply when moving to words that are used fewer times. 
Since these words have little to no ability to influence predictions, it makes sense that they can be safely removed from the dataset.

@@

@@

Model accuracy results after using the log-odds transformation are included in Figures \ref{figContextLogoddsSO} and \ref{figContextLogoddsT}.
Using the log-odds transformation technique has a small effect on model accuracy for StackOverflow (\numNoZero{.45} to \numNoZero{.47}) and minimal to no effect on Twitter (\numNoZero{.25} to \numNoZero{.25}).
When the technique is used and accuracy is examined for a model with only a single predictor, the transformation does not change accuracy.
When predictors are combined and the full model is examined, the transformation is in the direction of slightly increasing accuracy, at least for the StackOverflow dataset.
However, any improvement when using the transformation is minimal.

@@

There may be a slight edge in increased accuracy when a log-odds transformation is used for the StackOverflow dataset.
However, that result is not statistically reliable for the sample size used in this analysis (confidence intervals overlap in Figure \ref{figContextLogoddsSO}),
and even if present the overall change in accuracy is small (\numNoZero{.45} to \numNoZero{.47}).
Nonetheless, it does seem appropriate to convert the context to a log-odds adjustment value when context is added as an additional term to the random permutation model.
Since performance does not decrease when the transformation is made, may slightly increase,
and leads to a more natural interpretation of each model term as a log-odds value, it is reasonable to include this step for the random permutation model.
Future research could explore more improved methods to properly combine the terms.

@@

Model accuracy results after incorporating word order into the random permutation model are included in Figure \ref{figContextOrder}.
All bar plots that include an order component where ``window'' or ``direction'' is not included in the title use the standard ordering method (no direction or windowing, all position information is included) 
This is the default ordering method used, so the names for these bar plots were kept consistent to the names used in other figures so that comparisons could be made across figures if necessary
(similar to what was done for the default row size for the random permutation model).
Base models that do not use entropy weighting were also included so that effect sizes could be compared between entropy weighting and adding word order information.

@@

Also, the reason why the direction version of ordering is the best predictor of the three ordered components is most likely because order information does not have a large effect,
so the two representations for words to the left and right of a tag are highly correlated.
This means that this direction ordered component is essentially composed of all the co-occurrence observations in the orderless component after being randomly sampled and partitioned into two separate representations.
The co-occurrences in these representations are highly correlated with each other, and highly correlated with the orderless component,
which is why model accuracy is similar for the orderless component and direction ordered component, and why accuracy does not improve when adding the direction ordered component to the orderless component.

@@

All of the methodological and architectural tests were done on the Twitter popular-hashtags dataset and the StackOverflow randomly-sampled dataset.
For these tests, a logistic regression statistical technique is used to determine the optimal weight for each model component.
A regression is done for each run in the dataset, and since multiple runs were used for the StackOverflow and Twitter datasets, multiple samples of coefficient weights for each model component were computed.
The variance of the weights for each component show how likely it is that the regression is overfitting the data,
and the mean shows the best estimate weight of each component relative to the other.

@@

Coefficients for each model component of the full models are included in Figures \ref{figContextCoeffSO} and \ref{figContextCoeffT}.
Error bars represent the standard deviation of coefficient values for each component.
The standard deviation is used instead of the confidence interval of the mean so that the plots show the overall stability of each coefficient across the different runs.
The range of the distribution of coefficient values within a component is much more narrow than the range of the mean coefficient values between the components of each model.
This shows that the model is not being overfit, as the weights for each component are relatively stable across the different runs.

>>>>

In order to best combine these predictors, a logistic regression statistical technique similar to \textcite{Stanley2013} was used to determine the most optimal weights for each term.
\textcite{Stanley2013} weighted each term in the total activation equation Table \ref{tabModACTRModel}) to maximize model accuracy.
\citeAuthor{Stanley2013} found that the optimal weights for the StackOverflow model for the prior term, title context term, and body context term were \num{.62}, \num{.93}, and \num{1.75} respectively.

The optimal weights for each model component are computed in the same manner as \textcite{Stanley2013}:
When a user creates a tag for a post, a retrieval request for the model is made.
For each request, the model returns a set of tags (all tags that have been observed for that user in the past) and activations associated with each tag.
An activation value is computed for each model component (e.g., prior tag use, context) for each tag.
These values are recorded, and tag instances that match what the author actually tagged are marked as a 1, while all others are marked with a 0.
This process is repeated across all posts where a user chooses a tag, and across all users in the dataset.
Once all of the results are aggregated, a logistic regression is run where the optimal weights for each model component are found that maximize the model's ability to correctly label tags as 0 or 1 based on total activation.

@@

A simplified version of \citeauthor{Stanley2013}'s method was used for the results for this research.
Instead of subtracting off the mean total activation for the top 5 tags for each post, the process is done in isolation for each model component.
So for the prior component, the activation value used in the logistic regression is the prior activation with the mean of the top 5 prior activations subtracted from this value.
The same process is used for the context component.
Decoupling the offset term and computing an offset for each model component in isolation means that an iterative approach is no longer necessary,
since the optimal weights of the terms are no longer needed when computing the offset.

@@

The context component for both the random permutation and Bayesian model is based on the same co-occurrence matrix of words and observed tags.
Different size matrices were analyzed, ranging from \num{1000}, \num{10000}, \num{100000}, \num{1000000}, and \num{3000000} posts.
The matrix for \num{3000000} posts was only used for Twitter, since the number of words in a StackOverflow post is much higher than Twitter on average,
and the space and computational time required when using a co-occurrence matrix of \num{3000000} posts for StackOverflow is too large for a current high-performance desktop, even with highly optimized representations.
Already \num{835500000} total co-occurring word tag observations were used to build a co-occurrence matrix of \num{1000000} StackOverflow posts.
It was also the case that \num{1000000} posts for StackOverflow was already around $1/7$ of the total posts created on the site,
so it is reasonable to assume that the results would not change greatly for StackOverflow if $3/7$ of the total posts created were used to build the co-occurrence matrix instead,
especially since \num{835500000} co-occurrences were already used with \num{1000000} posts.

@@

The impact of adding the offset to each of the models for StackOverflow and Twitter is shown in Figures \ref{figContextOffsetSO} and \ref{figContextOffsetT}.
In both plots, if the model name includes ``full'' then all model components are included.
When the model components are enumerated, then at least one of the components is left out.
The random permutation and Bayesian models are plotted alongside each other so that comparisons across the two model types can be done easily.
So, for example, the ``standard prior model relaxed across posts without offset'' means that only the prior model component was used and the offset for that component was not subtracted off when determining activation.
As another example, the ``Bayes only orderless context'' means that only the context component of the Bayesian model was used (along with the offset), and that no order information was used for that contextual component term.

@@

The random permutation model in particular is greatly affected by the offset term, for both the StackOverflow and Twitter.
This suggests that the mean activation for the random permutation model for the top few tags in each post can vary greatly across posts.
Only if this mean activation is subtracted will the logistic regression model generate optimal weights and predictions that are comparable to the Bayesian model when model accuracy relaxed across posts is examined.

@@

One simple and likely explanation is that there are posts where a large set of tags have high activation,
but the author is choosing to use only a fixed small set of the top tags for each post, regardless of the activation values of the top tags.
The author determines the number of tags to use for a post based on competing goals of tagging posts an not overly saturating a post with tags.
For example, the author may be writing a question on StackOverflow about \emph{javascript}, and a large set of related tags are retrieved from declarative memory that are all above the retrieval threshold
(e.g., \emph{javascript}, \emph{dom}, \emph{svg}, \emph{html}, \emph{jquery}, \emph{css}),
but the author only chooses to use the tags \emph{javascript}, \emph{dom}, and \emph{svg}, since he has decided to tag this post with three tags, and those are the three tags with the highest activation.
Adding the offset term into the model is a way to implement a simple version of this strategy where the author is actively choosing to use only a small set of tags for each post.
Also, this type of strategic behavior of limiting the total number of chosen tags could be easily implemented in the production system of ACT-R.

@@

The four subsets were collected across a period of one month.
Each was collected sequentially, and about one subset was collected per week.
The hashtags used in each subset were chosen by scraping a site that published the current trending hashtags for each city.
Before starting to collect for each subset, the current trending popular hashtags for the 400 most populous US cities were collected, and then 400 popular hashtags were randomly sampled from this set.
Only 400 were selected since this is the maximum that the Twitter API can monitor at one time.

@@

Model accuracy results for components of both the random permutation and Bayesian models grouped by Twitter popular-hashtags subset are depicted in Figure \ref{figContextSubsets}.
Accuracy is affected significantly by subset ($F(3, 340) = 764, p < .001, \eta ^ {2} = .12$), model ($F(4, 340) = 3617, p < .001, \eta ^ {2} = .77$),
and the interaction between model and subset ($F(12, 340) = 142, p < .001, \eta ^ {2} = .09$).
However, the effect size of model type on accuracy is \num{8.6} times larger than the interaction term ($\eta ^ {2} = .77$ versus $\eta ^ {2} = .09$).
This shows that the performance of a model relative to the other models remains consistent across the four subsets.
Further, the effect size of model type is \num{6.3} times larger than the effect of Twitter subset ($\eta ^ {2} = .77$ versus $\eta ^ {2} = .12$).
This shows that not only is relative model performance maintained across Twitter subsets, but the exact value of model accuracy for each model remains reasonably consistent across subsets.

@@

The method of handling stop words has been shown to influence model accuracy \parencite{Sahlgren2008,Stanley2013}, so this was the first architectural concern that was examined.
\textcite{Sahlgren2008} looked at several ways to handle the commonly-occurring stop words for the random permutation model:
A data-driven frequency-weighted approach was tried, along with using a previously-generated stoplist, and no stop word removal at all.
Removing the high-frequency words in the dataset showed the highest performance increase compared to no stop word removal, and using a previously-generated stoplist hardly increased performance.
However, \citeauthor{Sahlgren2008} did not try to weight the stop words and only tried methods to remove them.
So alongside looking at frequency weighting, previously generated, and no stop word removal, \textcite{Stanley2013}'s method of attenuating stop words based on entropy was also explored.

@@

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{memMatSO-crop.pdf}}}
  \caption{
    Variance in observation counts of words for each tag for StackOverflow.
    Plots are shown for the four different methods for handling stop words.
    Each plot contains the standard deviation of the total counts for each word in context as a function of hashtag.
    High values mean that there are context words for a hashtag that have a high number of counts relative to the counts for all other context words for that hashtag.
  }
  \label{figContextCutoffSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.6}{\resizebox{\linewidth}{!}{\includegraphics{memMatT-crop.pdf}}}
  \caption{
    Variance in observation counts of words for each tag for Twitter.
  }
  \label{figContextCutoffT}
\end{figure}

@@

The three stop word techniques were then tested for the random permutation model on the Twitter dataset, and the results are depicted in Figure \ref{figContextStopRPT}.
For the random permutation model for Twitter, the entropy weighting technique is the best method for handling stop words (\numNoZero{.25} to \numNoZero{.26}).
Removing stop-words based on a predetermined list actually decreases accuracy (\numNoZero{.25} to \numNoZero{.23}), and using data-driven frequency filtering has only a small to no effect (\numNoZero{.25} to \numNoZero{.25}).

@@

Since accuracy measurements when using a predetermined list to remove stop words for the random permutation model were much worse than the frequency and entropy methods, this method was not examined for the Bayesian model.
The results for the frequency and entropy techniques for the Bayesian model on the StackOverflow dataset are depicted in Figure \ref{figContextStopBSO}.

@@

\subsection{Corpus Size}

The number of documents used to build the co-occurrence matrix has been shown to influence model accuracy \parencite{Sahlgren2008}, so this was the second architectural concern that was examined.
The default number of documents used to build the co-occurrence matrix was \num{1000000} for StackOverflow and \num{3000000} for Twitter.
In order to see how accuracy changed as function of corpus size, 
co-occurrence matrices for a range of smaller corpus sizes were built.
Both the random permutation and Bayesian models were tested on all corpus sizes.

@@

Model accuracy as a function of co-occurrence matrix size for StackOverflow is depicted in Figure \ref{figContextDocumentSizeSO}.
Accuracy improves for both the Bayesian and random permutation models as the size of the documents used to generate the co-occurrence matrix increases.
However, model accuracy using the entropy weighting technique plateaus and slightly decreases for the largest corpus size for the random permutation model, while the frequency technique only begins to plateau. 
The Bayesian model does not plateau and accuracy continues to improve as corpus size increases.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-freqVsEntropyBySizeSO-crop.pdf}}}
  \caption{
    Effect of size of co-occurrence matrix for StackOverflow.
    Error bars represent the 95\% bootstrapped confidence interval for the mean model accuracy across all runs in dataset.
  }
  \label{figContextDocumentSizeSO}
\end{figure}

@@

It is likely that the random permutation model is starting to saturate when entropy weighting is used for the largest corpus size for StackOverflow.
Saturation happens when certain words co-occur with a tag much more often than all of the other words.
This introduces range effects when the correlation is computed, which ends up driving all of the correlations near one, and consequently decreases discrimination and accuracy.
Saturation happens when entropy weighting is used because the non-predictive words are only attenuated and not removed, and this attenuation is not enough to overcome the range effects that grow with corpus size.

@@

The overall trend of increasing accuracy with corpus size is present for Twitter as well.
Both entropy weighting and frequency filtering in Figure \ref{figContextDocumentSizeT} plateau for the random permutation model with increasing corpus size.
Once again, the Bayesian model continues to improve with corpus size.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-freqVsEntropyBySizeT-crop.pdf}}}
  \caption{
    Effect of size of co-occurrence matrix for Twitter.
    Error bars represent the 95\% bootstrapped confidence interval for the mean.
  }
  \label{figContextDocumentSizeT}
\end{figure}

@@

It is interesting to compare model accuracy between the Bayesian and random permutation model at the smallest and largest corpus sizes for both StackOverflow and Twitter.
At smaller corpus sizes, the random permutation model outperforms the Bayesian model (slightly for Twitter, dramatically for StackOverflow), and this performance difference deteriorates as corpus size increases.
In other words, the Bayesian model needs larger co-occurrence matrices than the random permutation model to work properly.
As the size of the dataset increases, the compression may start to lose crucial information, and the uncompressed Bayesian model should be used.
As the size of the dataset decreases, the noise and crosstalk introduced by the compression for the random permutation model is actually beneficial, and the compressed random permutation model should be used. 
This noise is beneficial because it helps soften spurious $S_{ji}$ values when the counts for each individual cell in the co-occurrence matrix are still volatile, which happens at smaller corpus sizes.

This result has important implications.
The corpus size is rarely chosen, and more likely constrained by the number of documents in the dataset being studied.
If that dataset is relatively small, it may be better to use the compressed random permutation model than the Bayesian model, and vice-versa if the dataset is large.

However, corpus size is not the only factor that determines whether the Bayesian model or random permutation model will perform better.
For example, the corpus size where the Bayesian model begins to outperform the random permutation model is quite different for StackOverflow and Twitter.
This is because the number of observations used to generate the co-occurrence matrix is a function of four components:
corpus size, number of words in each document, total number of unique tags, and number of tags used per document.
The average number of tags used per post for StackOverflow and Twitter were the same order of magnitude (around 3 for StackOverflow, slightly less for Twitter).

However, the average number of words in a StackOverflow post is much greater than the 140 character limit used for tweets.
More words per post means that the number of observations per cell in the co-occurrence matrix grows more quickly with corpus size.
The Bayesian model is more likely to perform better with datasets like StackOverflow that have these larger corpus sizes.

@@

The compressed random permutation model should perform better with smaller corpus sizes, less words per document, more unique tags, and fewer number of tags per post.
However, since there are so many factors that determine whether the Bayesian or random permutation model will perform better,
and only two different datasets were examined in this research,
it is difficult to make any specific recommendations as far as exact transition cut points (e.g., corpus size, words per document) where either the Bayesian or random permutation model should be used.
Also, it is likely that the specific domain being studied interacts with the factors already mentioned to determine which model is better for that domain.
Nevertheless, if a researcher is working in a domain with limited data (e.g., small corpus size, large tag space) that produces a sparse co-occurrence matrix,
then it may be worthwhile to experiment with using a compressed random permutation model instead of the full Bayesian model.

@@

Results for using different levels of compression for the random permutation model for the StackOverflow dataset are depicted in Figure \ref{figContextDimSO}.
In the figure, the model name that does not have the number of rows in the matrix specified is the \num{2048}-row matrix.
This was done so that names in all of the plots would remain consistent across all plots, and the \num{2048}-row matrix is the size used for the random permutation model for all other results.
The plot is also broken out for different size datasets used to build the co-occurrence matrix.

@@

Reducing compression to only 100 rows in the representation has a strong negative effect on accuracy (\numNoZero{.60} to \numNoZero{.55} for the \num{1000000} document corpus size).
But \num{2048} rows is sufficient for these datasets,
as increasing the number of rows to almost an order of magnitude higher (\num{10000}) has little to no positive impact on accuracy (\numNoZero{.60} to \numNoZero{.60} for the \num{1000000} corpus size).

Results are similar for Twitter.
Figure \ref{figContextDimT} shows the same negative impact when reducing from \num{2048} to \num{100} (\numNoZero{.26} to \numNoZero{.24} for the \num{3000000} corpus size),
and little to no impact when increasing from \num{2048} to \num{10000} (\numNoZero{.26} to \numNoZero{.26} at \num{3000000}).
This results are consistent across all corpus sizes used to build the co-occurrence matrix.

@@

The fact that the random permutation model only needs around \num{2048} rows to represent all of the words in the Twitter and StackOverflow datasets is impressive.
Twitter has around \num{2383000} unique words for the \num{3000000} tweets in each of the popular-users datasets.
StackOverflow has \num{5848000} unique words for the \num{1000000} posts used to generate the co-occurrence matrix.
So it is impressive that only \num{2048} rows are needed to represent most of the variance from all of the words in these co-occurrence matrices.
This is likely because word use frequency for StackOverflow and Twitter approximately follows Zipf's law.
\textcite{Stanley2013} showed that frequency of tag use for StackOverflow approximately follows a Zipf's law distribution.
This means that if the words are rank sorted by number of times they are used, the frequency of word use drops off sharply when moving to words that are used fewer times. 
Since these words have little to no ability to influence predictions, it makes sense that they can be safely removed from the dataset.

@@

For example, say that the model is choosing between a set of tags, and those tags have a mean correlation of .2 with context and a standard deviation of 0.1.
If a tag in the set has correlation of .2 with context, then approximately half of the observed tags have a correlation lower than this tag.
So the one-tailed cumulative distribution value for this tag is .5.
If a tag in the set has a correlation of .3, then approximately half plus .34 (cumulative distribution of normal curve from mean to 1 standard deviation outward) of the observed tags have a lower correlation.
So the one-tailed cumulative distribution value for this tag is .84.

@@

Model accuracy results after using the log-odds transformation are depicted in Figures \ref{figContextLogoddsSO} and \ref{figContextLogoddsT}.
Using the log-odds transformation technique has a small effect on model accuracy for StackOverflow (\numNoZero{.45} to \numNoZero{.47}) and minimal to no effect on Twitter (\numNoZero{.25} to \numNoZero{.25}).
When the technique is used and accuracy is examined for a model with only a single predictor, the transformation does not change accuracy.
When predictors are combined and the full model is examined, the transformation is in the direction of slightly increasing accuracy, at least for the StackOverflow dataset.
However, any improvement when using the transformation is minimal.

@@

There may be a slight edge in increased accuracy when a log-odds transformation is used for the StackOverflow dataset.
However, that result is not statistically reliable for the sample size used in this analysis (confidence intervals overlap in Figure \ref{figContextLogoddsSO}),
and even if present the overall change in accuracy is small (\numNoZero{.45} to \numNoZero{.47}).
Nonetheless, it does seem appropriate to convert the context to a log-odds adjustment value when context is added as an additional term to the random permutation model.
Since performance does not decrease when the transformation is made, may slightly increase,
and leads to a more natural interpretation of each model term as a log-odds value, it is reasonable to include this step for the random permutation model.
Future research could explore additional methods to properly combine the terms.

@@

Model accuracy results after incorporating word order into the random permutation model are depicted in Figure \ref{figContextOrder}.
All bar plots that include an order component where ``window'' or ``direction'' is not included in the title use the standard ordering method (no direction or windowing, all position information is included) 
This is the default ordering method used, so the names for these bar plots were kept consistent to the names used in other figures so that comparisons could be made across figures if necessary
(similar to what was done for the default row size for the random permutation model).
Base models that do not use entropy weighting were also included so that effect sizes could be compared between entropy weighting and adding word order information.

@@

Also, the reason why the directional version of ordering is the best predictor of the three ordered components is most likely because order information does not have a large effect,
so the two representations for words to the left and right of a tag are highly correlated.
This means that this directionally-ordered component is essentially composed of all the co-occurrence observations in the orderless component after being randomly sampled and partitioned into two separate representations.
The co-occurrences in these representations are highly correlated with each other, and highly correlated with the orderless component,
which is why model accuracy is similar for the orderless component and direction ordered component, and why accuracy does not improve when adding the direction ordered component to the orderless component.

@@

All of the methodological and architectural tests were done on the Twitter popular-hashtags dataset and the StackOverflow randomly-sampled dataset.
For these tests, a logistic regression statistical technique was used to determine the optimal weight for each model component.
A regression was done for each run in the dataset, and since multiple runs were used for the StackOverflow and Twitter datasets, multiple samples of coefficient weights for each model component were computed.
The variance of the weights for each component show how likely it is that the regression is overfitting the data,
and the mean shows the best estimate weight of each component relative to the other.

@@

Coefficients for each model component of the full models are depicted in Figures \ref{figContextCoeffSO} and \ref{figContextCoeffT}.
The range of the distribution of coefficient values within a component is much more narrow than the range of the mean coefficient values between the components of each model.
This shows that the model is not being overfit, as the weights for each component are relatively stable across the different runs.
